---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Heather Hawkins"
date: "01-04-23"
output: github_document

---

### Load packages and data



```{r load-packages, message = FALSE}
library(rvest)
library(skimr)
library(glue)
library(tidyverse) 
library(usethis)
```


### Exercise 1

```{r start}
# setting the url
first_url <- "https://collections.ed.ac.uk/art/search/*:*/Collection:%22edinburgh+college+of+art%7C%7C%7CEdinburgh+College+of+Art%22?offset=0"

# reading the html page
page <- read_html(first_url)

# Scraping titles

titles <- page %>%
  html_nodes(".iteminfo") %>%
  html_node("h3 a") %>%
  html_text() %>% 
  str_squish()

# Scraping links

links <- page %>%
  html_nodes(".iteminfo") %>%   # same nodes
  html_node("h3 a") %>%         # as before
  html_attr("href") %>%         # but get href attribute instead of text
  str_replace(pattern =".", replacement = "https://collections.ed.ac.uk") #replacing link

```


### Exercise 2
```{R 2}
# scraping artists 

artists <- page %>%
  html_nodes(".iteminfo") %>%
  html_node(".artist") %>%
  html_attr("title")
```


### Exercise 3

```{R 3}
first_ten <- tibble(
  title = titles,
  artist = artists,
  link = links)

first_ten
```
### Exercise 4

```{R scrape_2}
second_url <- "https://collections.ed.ac.uk/art/search/*:*/Collection:%22edinburgh+college+of+art%7C%7C%7CEdinburgh+College+of+Art%22?offset=10"

page2 <- read_html(second_url)


titles2 <- page2 %>%
  html_nodes(".iteminfo") %>%
  html_node("h3 a") %>%
  html_text() %>%
  str_squish()

links2 <- page2 %>%
  html_nodes(".iteminfo") %>%
  html_node("h3 a") %>%
  html_attr("href") %>%
  str_replace(".", "https://collections.ed.ac.uk/art/")

artists2 <- page2 %>%
  html_nodes(".iteminfo") %>%
  html_node(".artist") %>%
  html_text() %>%
  str_squish()

second_ten <- tibble(
  title = titles2,
  artist = artists2,
  link = links2)

second_ten
```

### Exercise 5

```{r scrape_funtion}
# test

add_two <- function(x){
  x + 2
}

add_two(3)

add_two(10)

# function: scrape_page --------------------------------------------------------

scrape_page <- function(url){
  # read page
  page <- read_html(url)
  
  # scrape titles
  titles <- page %>%
    html_nodes(".iteminfo") %>%
    html_node("h3 a") %>%
    html_text() %>% 
    str_squish()
  
  # scrape links
  links <- page %>%
    html_nodes(".iteminfo") %>%   # same nodes
    html_node("h3 a") %>%         # as before
    html_attr("href") %>%         # but get href attribute instead of text
    
    str_replace(pattern =".", replacement = "https://collections.ed.ac.uk") #replacing
  
  # scrape artists 
  names <- page %>% 
    html_nodes(".iteminfo") %>% 
    html_node(".artist") %>% 
    html_attr("title")
  
  # create and return tibble
  tibble(title = titles, 
         name = names,
         link = links)
  
}
```

### Exercise 6

```{r testing}

scrape_page(first_url)
scrape_page(second_url)

```

### Exercise 7

```{r list-urls}
root <- "https://collections.ed.ac.uk/art/search/*:*/Collection:%22edinburgh+college+of+art%7C%7C%7CEdinburgh+College+of+Art%22?offset="
numbers <- seq(from = 0, to = 3010, by = 10)
urls <- glue("{root}{numbers}")
```

### Exercise 8
]
uoe_art <- map_dfr(urls, scrape_page)

]

### Exercise 9

--

write_csv(uoe_art, file = "uoe-art.csv")
-

### Exercise 10

```{r separate-titleanddate, error = TRUE}
uoe_art <- read_csv("uoe-art.csv")
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, name, year, link)
```

We have a warning bc some titles did not have the year in (). Bc of this, they are labeled as NA

### Exercise 11

```{R skimming-like-swimming}
skim(uoe_art)
```
115 have artist info missing and 1431 have year missing

### Exercise 12
```{r}

uoe_art %>%
  ggplot(aes(x=year)) + geom_bar()

uoe_art %>% filter(year <  50)
```

### Exercise 13

The Death Mask is labelled as the year "2", it was actually made in 1964....

```{R fixxinngg}
uoe_art<-uoe_art %>% mutate(year = if_else(year == 2, 1964, year))

ggplot(data = uoe_art, aes(x = year)) + geom_bar(binwidth = 100)

##YAY
  
```


### Exercise 14
```{R ImTired}
uoe_art %>% count(name) %>% arrange(desc(n)) %>% head(10)
```
The MOST commonly featured "artist" is "unknown"- meaning that many pieces do not have a name attached. the second in Emma Gilles- Idk why they have so much of her, I was guessing she was born/lived near there or something- and I was right!! (after googling of course)

### Exercise 15
```{r last}
uoe_art %>% 
  filter(
    str_detect(title , "child") |
      str_detect(title , "Child")
  )
```
There are 11 art titles that contain the word child.
